Distrivia: A Distributed Trivia Game

### 2011-05-11 papers/phase-three/paper.tex
Paper: Fix typo
Paper: Fix double the

\subsection{Server Applications}
% TODO Finish
The server application handles requests from the user via the load sharers.
Interpretation of the client messages and replies are handled by the applications. There is one application per server processing requests and responding via https messages with JSON objects.
The server application supports the following features:
\begin{itemized}
\item Client registration
\item Login
\item Query games status
\item Joining public games
\item Joining private games
\item Creating private games
\item Question retrieval
\item Question answering
\item Global leaderboard
\end{itemized}

\subsection{Load Sharers}
The load sharers act as an agent between the clients and the servers to ensure reliable, fast communication.
Messages are relayed through the load sharers from the client.
Once received, the load sharer will pass the message onto any active server or, if there are none active, it will deliver the message to a hot spare server.
This is an important part of the distributed system in keeping network traffic down on the the active servers so they may serve requests faster and for making sure the server attempting to service the client's request is active and able to process the message.
They attempt to connect to a server twice in a one second period before deeming it dead and removing it from its list of servers to direct clients towards.
This is important to make sure that any servers that go down do not receive further communication attempts.

>>>>

\subsection{Server Applications}
% TODO Finish
The server application handles requests from the user via the load sharers.
Interpretation of the client messages and replies are handled by the applications. There is one application per server processing requests and responding via https messages with JSON objects.
The server application supports the following features:
\begin{itemize}
\item Client registration
\item Login
\item Query games status
\item Joining public games
\item Joining private games
\item Creating private games
\item Question retrieval
\item Question answering
\item Global leaderboard
\end{itemize}

\subsection{Load Sharers}
The load sharers act as an agent between the clients and the servers to ensure reliable, fast communication.
Messages are relayed through the load sharers from the client.
Once received, the load sharer will pass the message onto any active server or, if there are none active, it will deliver the message to a hot spare server.
This is an important part of the distributed system in keeping network traffic down on the active servers so they may serve requests faster and for making sure the server attempting to service the client's request is active and able to process the message.
They attempt to connect to a server twice in a one second period before deeming it dead and removing it from its list of servers to direct clients towards.
This is important to make sure that any servers that go down do not receive further communication attempts.
